Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-12 paper/virtual_cytoplasm_v2.tex
shrinking volume and density plots added

< SHRINKING PLOTS SHOWING BOX VOLUME/DENSITY ? >

@@

\begin{figure}

\includegraphics[scale=0.6]{msd.pdf}
\caption{Diffusion coefficient of crowders from single molecule simulations (blue bars) and cytoplasm simulations (orange bars).}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{rdf_mg.pdf}
\caption{Radial distribution function showing the probability of finding a metabolite or an RNA around MG2+.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.6]{shrinking_volume.pdf} 
\includegraphics[scale=0.6]{shrinking_density.pdf} 
\caption{A) The volume of the box with length size of $L=35 \,\, nm$ reduces during the energy minimization in the first $300 \,\, ps$ B) The density of the same box increases within the first $300\,\, ps$. The repeated experiments are shown in different colors. }
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{msd.pdf}
\caption{Diffusion coefficient of crowders from single molecule simulations (blue bars) and cytoplasm simulations (orange bars).}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{rdf_mg.pdf}
\caption{Radial distribution function (rdf) showing the probability of finding a metabolite or an RNA around MG2+. The inset plot shows the rdf for short distance ($ r < 0.6 \,\, nm$)}
\end{figure}
